A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-12 manuscript.Rmd
hide code for plot

```{r}
res <- read_csv(here::here("data", "simulation_results.csv"), col_types = "ddddd")
```

```{r}
res_interval <- res %>%
  select(n_obs, std_estimate) %>% 
  filter(!is.na(std_estimate)) %>% 
  group_by(n_obs) %>% 
  summarise(interval = list(interval(std_estimate, seq(0.05, .2, 0.01))), 
            .groups = "drop", median = median(std_estimate)) %>% 
  unnest(c(interval)) %>% 
  mutate(width = upper - lower, perc = 1 - alpha) %>% 
  group_by(alpha) %>% 
  arrange(n_obs) %>% 
  mutate(across(c(width, upper, lower),
                ~slide_dbl(.x, mean, na.rm = TRUE, .before = 2, .after = 0, .complete = FALSE))) %>% 
  ungroup() %>% 
  arrange(perc)
```

```{r}
choosen_perc <- .8
choosen_width <- .2
true_diff <- .2
minn <- filter(res_interval, perc == choosen_perc, width < choosen_width) %>% 
  filter(n_obs == min(n_obs))
sim_n <- pull(res, n_obs)
sim_nmax <- max(sim_n)
sim_n_unique <- unique(sim_n)
sim_nstep <- sim_n_unique[2] - sim_n_unique[1]
```

```{r}
plot_interval <- res_interval %>%
  ggplot(aes(
    n_obs,
    ymin = lower,
    ymax = upper,
    fill = perc,
    group = alpha
  )) +
  geom_ribbon() +
  geom_line(aes(y = median), color = "white") +
  geom_hline(yintercept = true_diff, linetype = "dotted") +
  scale_fill_viridis_c(
    begin = 1,
    end = 0,
    breaks  = 1 - seq(0.05, .2, 0.05),
    labels = . %>% scales::percent(accuracy = 1)
  ) +
  scale_y_continuous(n.breaks = 10) +
  scale_x_continuous(breaks = seq(0, sim_nmax, sim_nstep * 10)) +
  theme_minimal() +
  labs(x = "N per Group", y = "Standardized Effect Size") +
  theme(legend.title = element_blank()) +
  NULL
```

```{r}
plot_width <- res_interval %>%
  ggplot(aes(n_obs, width, color = perc, group = perc)) +
  geom_line() +
  geom_point(
    data = minn,
    size = 3,
    color = "black",
    shape = 3
  ) +
  scale_color_viridis_c(
    begin = 1,
    end = 0,
    breaks = 1 - seq(0.05, .2, 0.05),
    labels = . %>% scales::percent(accuracy = 1)
  ) +
  theme_minimal() +
  scale_y_log10(breaks = seq(0, 0.8, .1)) +
  scale_x_continuous(breaks = seq(0, sim_nmax, sim_nstep * 10)) +
  labs(x = "N per Group", y = "Width of quantile\n(Standardized Effect Size)") +
  theme(legend.title = element_blank()) +
  NULL
```

```{r}
simulation_plot <- plot_interval +
  theme(axis.text.x = element_blank(), axis.title.x = element_blank()) + 
  plot_width +
  plot_layout(nrow = 2, guides = 'collect') +
  plot_annotation(tag_levels = 'A')
```

```{r}
simulation_plot
```

Plot A depicts the range of effect sizes we observed in the simulation, where the colour encodes the density.
The light yellow interval shows where 80% of the estimates land.
The dotted line represents the simulated true effect size; the white line shows the median observed effect sizes.

Plot B represents the width of the interval shown in Plot A on a logarithmic scale.
The cross shows the minimum required sample size so that 80% of the estimates land in a range of +/- .1.

>>>>

```{r, include=FALSE}
res <- read_csv(here::here("data", "simulation_results.csv"), col_types = "ddddd")
```

```{r, include=FALSE}
res_interval <- res %>%
  select(n_obs, std_estimate) %>% 
  filter(!is.na(std_estimate)) %>% 
  group_by(n_obs) %>% 
  summarise(interval = list(interval(std_estimate, seq(0.05, .2, 0.01))), 
            .groups = "drop", median = median(std_estimate)) %>% 
  unnest(c(interval)) %>% 
  mutate(width = upper - lower, perc = 1 - alpha) %>% 
  group_by(alpha) %>% 
  arrange(n_obs) %>% 
  mutate(across(c(width, upper, lower),
                ~slide_dbl(.x, mean, na.rm = TRUE, .before = 2, .after = 0, .complete = FALSE))) %>% 
  ungroup() %>% 
  arrange(perc)
```

```{r, include=FALSE}
choosen_perc <- .8
choosen_width <- .2
true_diff <- .2
minn <- filter(res_interval, perc == choosen_perc, width < choosen_width) %>% 
  filter(n_obs == min(n_obs))
sim_n <- pull(res, n_obs)
sim_nmax <- max(sim_n)
sim_n_unique <- unique(sim_n)
sim_nstep <- sim_n_unique[2] - sim_n_unique[1]
```

```{r, include=FALSE}
plot_interval <- res_interval %>%
  ggplot(aes(
    n_obs,
    ymin = lower,
    ymax = upper,
    fill = perc,
    group = alpha
  )) +
  geom_ribbon() +
  geom_line(aes(y = median), color = "white") +
  geom_hline(yintercept = true_diff, linetype = "dotted") +
  scale_fill_viridis_c(
    begin = 1,
    end = 0,
    breaks  = 1 - seq(0.05, .2, 0.05),
    labels = . %>% scales::percent(accuracy = 1)
  ) +
  scale_y_continuous(n.breaks = 10) +
  scale_x_continuous(breaks = seq(0, sim_nmax, sim_nstep * 10)) +
  theme_minimal() +
  labs(x = "N per Group", y = "Standardized Effect Size") +
  theme(legend.title = element_blank()) +
  NULL
```

```{r, include=FALSE}
plot_width <- res_interval %>%
  ggplot(aes(n_obs, width, color = perc, group = perc)) +
  geom_line() +
  geom_point(
    data = minn,
    size = 3,
    color = "black",
    shape = 3
  ) +
  scale_color_viridis_c(
    begin = 1,
    end = 0,
    breaks = 1 - seq(0.05, .2, 0.05),
    labels = . %>% scales::percent(accuracy = 1)
  ) +
  theme_minimal() +
  scale_y_log10(breaks = seq(0, 0.8, .1)) +
  scale_x_continuous(breaks = seq(0, sim_nmax, sim_nstep * 10)) +
  labs(x = "N per Group", y = "Width of quantile\n(Standardized Effect Size)") +
  theme(legend.title = element_blank()) +
  NULL
```

```{r, include=FALSE}
simulation_plot <- plot_interval +
  theme(axis.text.x = element_blank(), axis.title.x = element_blank()) + 
  plot_width +
  plot_layout(nrow = 2, guides = 'collect') +
  plot_annotation(tag_levels = 'A')
```

```{r, simulation-plot, echo=FALSE, fig.cap="*Plot A* depicts the range of effect sizes we observed in the simulation, where the colour encodes the density. The light yellow interval shows where 80% of the estimates land. The dotted line represents the simulated true effect size; the white line shows the median observed effect sizes. *Plot B* represents the width of the interval shown in Plot A on a logarithmic scale. The cross shows the minimum required sample size so that 80% of the estimates land in a range of +/- .1.  "}
simulation_plot
```
